Python as a machine learning language: experiences from the scikit-learn project

### 2013-06-12 paper.tex
avoid enumerate where not necessary

\texttt{Pipeline} objects are used for chaining multiple estimators into a
single one. This is useful since a machine learning workflow typically involves
a fixed sequence of steps in processing data (e.g., feature extraction,
normalization, feature selection, learning and making predictions).
A sequence of $N$ such steps can be combined into a composite object
called a \texttt{Pipeline}.
The first $N-1$ steps must be transformers
and the last can be either a predictor or a transformer.
Fitting a pipeline to a training set amounts, conceptually,
to the following recursive procedure:
\begin{enumerate}
  \item When only one step remains, call its \texttt{fit} method.
  \item Otherwise, fit the first step,
        use it to \texttt{transform} the training set
        and fit the rest of the pipeline with the transformed data.
\end{enumerate}
The pipeline exposes all the methods the last
estimator in the pipe exposes. That is, if the last estimator is a predictor,
the pipeline can itself be used as a predictor. If the last estimator is a
transformer, then the pipeline is itself a transformer. \textcolor{red}{TODO:
Talk about nested attribute syntax.}

>>>>

\texttt{Pipeline} objects are used for chaining multiple estimators into a
single one. This is useful since a machine learning workflow typically involves
a fixed sequence of steps in processing data (e.g., feature extraction,
normalization, feature selection, learning and making predictions). A sequence
of $N$ such steps can be combined into a composite object called a
\texttt{Pipeline}. The first $N-1$ steps must be transformers and the last can
be either a predictor or a transformer. Conceptually, fitting a pipeline to a
training set amounts to the following recursive procedure: i) when only one step
remains, call its \texttt{fit} method; ii) otherwise, fit the first step, use it
to \texttt{transform} the training set and fit the rest of the pipeline with the
transformed data.

The pipeline exposes all the methods the last
estimator in the pipe exposes. That is, if the last estimator is a predictor,
the pipeline can itself be used as a predictor. If the last estimator is a
transformer, then the pipeline is itself a transformer. \textcolor{red}{TODO:
Talk about nested attribute syntax.}
